Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-03 inc/hardware/laser/laser.tex
tweaks to the laser section

The second harmonic generation system now employs a 3mm non-critically phase matched LBO crystal. This has two benefits, in this geometry the walk-off angle between the fundamental and second harmonic is zero while the group velocity mismatch of 150fs ($\sim$ 50fs/mm) is much less than the pulse duration 250fs. Second, because the non-critically phase matched crystal is constantly held at a temperature above the boiling point of water, this prevents the deleterious absorption of water which is inherent in the hygroscopic crystal. In the place of the curved mirrors originally employed, this second harmonic system uses 75mm lenses to focus the laser into the crystal and collimate the output.

Although the laser system had been relatively robust, maintaining mode-locking was initially problematic. To prevent dust from entering interrupting mode locking, a dust cover was added above the laser cavity. More importantly, a 1.4mm aperture (approximately four times the HW1/eM beam width at the output coupler) was added to suppress higher-order transverse modes. As this is an additional loss in the cavity, the output coupler was changed from 93\% to 95\% reflectivity to maintain the soliton modelocking power.

>>>>

The second harmonic generation system now employs a 3mm non-critically phase matched LBO crystal.
This change has two benefits. 
First, in this geometry, the walk-off angle between the fundamental and second harmonic is zero, while the group velocity mismatch of 150fs ($\sim$ 50 fs/mm) is much less than the pulse duration 250fs. %TODO cite Koechner?
Second, because in this case, non-critically phase matching requires that the crystal is held at an elevated temperature, well above the boiling point of water, the deleterious absorption of water in the hygroscopic LBO crystal is prevented.
Note that additionally, in the place of the curved mirrors originally employed, the second harmonic system now uses 75mm lenses to focus the laser into the crystal and collimate the output.

Although the laser system had been relatively robust, maintaining mode-locking operation was initially problematic.
A cover was added above the laser cavity to prevent dust and air currents from interrupting mode locking.
More importantly, a 1.4mm aperture (approximately four times the HW1/eM beam width at the output coupler) was added to suppress higher-order transverse modes.
As this is an additional loss in the cavity, the output coupler was changed from 93\% to 95\% reflectivity to maintain the soliton modelocking power.
